%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

% modern font things
\usepackage{lmodern}
% special graphic characters
\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
% provides horizontal lines
\usepackage{titlesec}
% used to draw gradient for rule
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

% Line Spacing
\setstretch{0.96}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% custom colors
\definecolor{primarycolor}{RGB}{171,34,201}
\definecolor{fontcolor}{RGB}{60,60,60}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{primarycolor}\titlerule \vspace{-8pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label=,itemsep=-1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\%
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt,parsep=0pt,topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0pt}}
\newcommand{\resumeItem}[1]{
  \item\small{{#1}}
}

\newcommand{\skillsEntry}[2]{
    \item{
      \textbf{#1}{: #2}
    }
}

\renewcommand{\labelitemii}{$\circ$}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\color{fontcolor}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/beezow}{\Large Andrew \textcolor{primarycolor}{Zoghby}}} & \textcolor{primarycolor}{\faEnvelope[regular]} \href{mailto:dzoghby4@gmail.com}{dzoghby4@gmail.com}\\
   & \href{https://github.com/beezow}{\textcolor{primarycolor}{\faGithub[regular]} github.com/beezow}
\end{tabular*}
\vspace{-15pt}
\section{Personal Statement}
\small{% comment to skip the newline here
% silicon FW statement: Firmware Engineer specializing in bare metal environments and custom platform tooling. Proven track record of building software models and tools for rapid pre- and post-silicon debugging. Seeking to leverage expertise in Rust firmware, silicon bringup, and system design to build high-performance silicon platforms.
%
% platform FW statement:
Firmware Engineer specializing in bare metal environments and custom platform tooling. Proven track record of performing critical platform enablement and debugging complex FW/HW interactions. Seeking to leverage this expertise in Rust firmware and system bringup to enabled a team to launch new products.
}\vspace{-6pt}
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubHeading
      {Rivos / Meta \small\textmd{(via acquisition Dec 2025)}}{June 2022 - Present}
      {Firmware Engineer}{}
      \resumeItemListStart
        \resumeItem{Wrote a variety of RISC-V runtimes, including porting the open source Hubris \href{https://github.com/rivosinc/hubris}{\faLink[regular]} microkernel and its Humility \href{https://github.com/rivosinc/humility}{\faLink} debugger to RISC-V.}
        % \resumeItem{DDR5 Firmware and Bringup Lead}
        \resumeItem{Led firmware development for a first-generation DDR5 memory controller and PHY.}
        \resumeItemListStart
          \resumeItem{Integrated IP vendor C code directly into Rust based FW stack using a collection of FFI shim layers, allowing for quick rollout of vendor updates.}
          % \resumeItem{Built debug tooling for tuning memory controller timing parameters and all dependent values.}
          \resumeItem{Generated and debugged PHY loopback patterns for ATE testing environments.}
          \resumeItem{Built a testing framework to directly reuse production firmware against pre-si DV models and post-si bringup environments. Enabled seamless transition between pre-si, post-si, and production.}
          \resumeItem{Successful Linux boot in 2 weeks on first generation silicon, in thanks to decoupling DDR testing from other SoC functions, allowing DDR bringup to start day-zero.}
          \resumeItem{Interpreted JEDEC specifications and manufacturer datasheets to guarantee functionality and compliance across diverse DIMM variants.}
          \resumeItem{Used high-speed oscilloscopes and logic analyzers to debug termination impedances and protocol issues during bringup to support running at higher data rates.}
        \resumeItemListEnd
        % \resumeItem{Post Silicon Validation Platform Tooling}
        \resumeItem{Architected and led development of critical post-silicon tooling for controlling and debugging a first-generation server platform.}
        \resumeItemListStart
          \resumeItem{Successfully enabled in-depth remote debugging for a global workforce, requiring minimal in-person tasks.}
          \resumeItem{Created a machine-readable model of on-platform devices to dynamically change operations based on board configurations and user preferences, enabling flexible multi-configuration bringup with a simple UX.}
          \resumeItem{Implemented device drivers for on-board peripherals over JTAG, I\textsuperscript{2}C, I3C, SPI, and other interfaces, enabling board bringup, power sequencing and SoC debug infrastructure.  Required debugging analog and digital circuits for reset sequencing, bus interference, and margin issues.}
          \resumeItem{Debugged FTDI protocol issues using scopes and logic analyzers; fixes landed upstream to pyftdi and pyspiflash.}
        \resumeItemListEnd
      \resumeItemListEnd
      
    \resumeSubHeading
      {Micron}{Summer 2021}
      {Embedded System Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Overhauled protocols built on top of USB to utilize DMA for 99\% throughput performance improvement.}
        \resumeItem{Analyzed legacy test equipment FW to identify and fix newly exposed test escapes.}
      \resumeItemListEnd

    \resumeSubHeading
      {UIUC Field Robotics Engineering and Sciences Hub}{Spring 2021}
      {Robotics Engineering Undergraduate Research Assistant}{}
      \resumeItemListStart
        \resumeItem{Developed kinematic models of a tractor in Gazebo for efficient testing of algorithms without field testing.}
        \resumeItem{Collaborated with a team of research engineers to formulate motion planning algorithms.}
        \resumeItem{Fitted sensor package to tractor to feed motion control algorithms.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
      

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \skillsEntry{Languages}{Rust, C, Python, RISC-V Assembly}\vspace{-5pt}
    \skillsEntry{Protocols and Hardware}{JTAG, I\textsuperscript{2}C, I3C, SPI, UART, DDR5, Oscilloscopes, Logic Analyzers}\vspace{-5pt}
    \skillsEntry{Tools}{Git, Cargo, GDB, KiCad}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubHeading
      {University of Illinois Urbana-Champaign}{2018 -- 2022}
      {BS in Computer Engineering, Minor in Statistics}{3.88/4.0}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
